Comparison of ASVs and OTUs between PacBio and Ion Torrent

### 2019-06-10 writing/tech_compare.Rmd
Move guide line to have 0 intercept

asv_samp_plot %>%
  filter(is_057 > 0, pb_500 > 0) %>%
  ggplot(aes(x = is_057, y = pb_500)) +
  geom_point(alpha = 0.2) +
  scale_x_log10() +
  scale_y_log10() +
  xlab("Ion Torrent wells") +
  ylab("PacBio wells") +
  geom_rug(aes(y = pb_500, x = 1), sides = "l", alpha = 0.2,
           data = asv_samp_plot %>% filter(is_057 == 0)) +
  geom_rug(aes(y = is_057), sides = "b", alpha = 0.2,
           data = asv_samp_plot %>% filter(pb_500 == 0)) +
  stat_smooth(method = "loess", formula = y ~ x) +
  geom_abline(aes(intercept = mean(log10(pb_500)) -
                    mean(log10(is_057)), slope = 1),
              linetype = 2L, alpha = 0.5)

@@

otu_samp_plot %>%
  filter(is_057 > 0, pb_500 > 0) %>%
  ggplot(aes(x = is_057, y = pb_500)) +
  geom_point(alpha = 0.2) +
  scale_x_log10() +
  scale_y_log10() +
  xlab("Ion Torrent wells") +
  ylab("PacBio wells") +
  geom_rug(aes(y = pb_500, x = 1), sides = "l", alpha = 0.2,
           data = otu_samp_plot %>% filter(is_057 == 0)) +
  geom_rug(aes(y = is_057), sides = "b", alpha = 0.2,
           data = otu_samp_plot %>% filter(pb_500 == 0)) +
  stat_smooth(method = "loess", formula = y ~ x) +
  geom_abline(aes(intercept = mean(log10(pb_500)) -
                    mean(log10(is_057)), slope = 1),
              linetype = 2L, alpha = 0.5)
```

>>>>

asv_samp_plot %>%
  filter(is_057 > 0, pb_500 > 0) %>%
  ggplot(aes(x = is_057, y = pb_500)) +
  geom_point(alpha = 0.2) +
  scale_x_log10() +
  scale_y_log10() +
  xlab("Ion Torrent wells") +
  ylab("PacBio wells") +
  geom_rug(aes(y = pb_500, x = 1), sides = "l", alpha = 0.2,
           data = asv_samp_plot %>% filter(is_057 == 0)) +
  geom_rug(aes(y = is_057), sides = "b", alpha = 0.2,
           data = asv_samp_plot %>% filter(pb_500 == 0)) +
  stat_smooth(method = "loess", formula = y ~ x) +
  geom_abline(aes(intercept = 0, slope = 1),
              linetype = 2L, alpha = 0.5)

@@

otu_samp_plot %>%
  filter(is_057 > 0, pb_500 > 0) %>%
  ggplot(aes(x = is_057, y = pb_500)) +
  geom_point(alpha = 0.2) +
  scale_x_log10() +
  scale_y_log10() +
  xlab("Ion Torrent wells") +
  ylab("PacBio wells") +
  geom_rug(aes(y = pb_500, x = 1), sides = "l", alpha = 0.2,
           data = otu_samp_plot %>% filter(is_057 == 0)) +
  geom_rug(aes(y = is_057), sides = "b", alpha = 0.2,
           data = otu_samp_plot %>% filter(pb_500 == 0)) +
  stat_smooth(method = "loess", formula = y ~ x) +
  geom_abline(aes(intercept = 0, slope = 1),
              linetype = 2L, alpha = 0.5)
```
